Diversity and evolution of centromere repeats in the maize genome

### 2013-11-10 centc.tex
minor changes to text, new bibtex -PB
Addresses Added -PB

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
\jri{Please add addresses etc. Gaby, Jose, and Kevin all need to be listed as plant sciences as they were here when they did the work. we can ask them if they would like their other addresses ALSO listed (fine by me) but they need to have plant sciences too.  Put Junghua as Dept. of Plant Bio UGA.  Then make a separate one for Dept. Genetics UGA, and put Kelly as both.}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

@@

We used long-read Pacific Biosciences sequencing to verify that most CentC is in tandem arrays. We sequenced whole genome ($\approx 0.3$X \jri{I made up 0.3. can you estimate what this is? Just total Mb of data / genome size.}) libraries from 4 Zea species.  In spite of the low coverage, we recovered reads containing CentC sequence from all four taxa (Supplementary Table \jri{add}).  In one 6.7kb read from the maize reference line B73, for example, we identified approximately 40 independent CentC copies in tandem, and similar arrays were seen in all four Zea species analyzed.  These results show that overall structure of the repeats has been maintained for the approximately 140,000 years since the \emph{luxurians}-\emph{mays} divergence (Hanson et al. 1996; Ross-Ibarra et al. 2009) and that a majority of CentC is found in tandem arrays (\jri{add table ref}). \jri{this last sentence is a nice addition}

>>>>

\institute{Paul Bilinski : Kevin Distor : Jose Gutierez-Lopez : Gabriela Mendoza Mendoza : Jeffrey Ross-Ibarra\at
              Department of Plant Sciences, UC Davis\\
              Davis, California, 95616
              \and
              Jeffrey Ross-Ibarra\at
              The Genome Center and Center for Population Biology, University of California\\
              Davis, California, 95616\\
              \email{rossibarra@ucdavis.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Jinghua Shi : R. Kelly Dawe\at
           Department of Plant Biology, University of Georgia\\
	  Athens, Georgia, 30602
           \and
           R. Kelly Dawe\at
           Department of Genetics, University of Georgia\\
           Athens, Georgia, 30602\\
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor
\maketitle

@@

We used long-read Pacific Biosciences sequencing to verify that most CentC is in tandem arrays. We sequenced whole genome ($\approx 0.1$X ) libraries from 4 Zea species.  In spite of the low coverage, we recovered reads containing CentC sequence from all four taxa (Supplementary Table \jri{add}).  In one 6.7kb read from the maize reference line B73, for example, we identified approximately 40 independent CentC copies in tandem, and similar arrays were seen in all four Zea species analyzed.  These results show that overall structure of the repeats has been maintained for the approximately 140,000 years since the \emph{luxurians}-\emph{mays} divergence (Hanson et al. 1996; Ross-Ibarra et al. 2009) and that a majority of CentC is found in tandem arrays (\jri{add table ref}). \jri{this last sentence is a nice addition}
